**First high-frequency time series of carbonate chemistry in the Arctic**

### 2023-05-25 awipev-CO2_presentation.qmd
minor

***

@@

![ ](images/map_fransner.png){width="50%"}
![ ](images/pH_fransner.png){width="50%"}

***

# **Study location** 
![ ](images/map_platt.png)

@@

***

:::: {.blackbox data-latex=""}
## **Instrumental set-up**

@@

:::: {style="display: flex;"}
::: {class='col-md-4'}
![ ](images/container.png)
:::

::: {class='col-md-4'}
![ ](images/intake.png)
:::

::: {class='col-md-4'}
![ ](images/ferrybox.jpg)
:::
::::

## **Instruments on the REMOS**
![ ](images/seafet.png)

***

<!-- # No longer in real-time: https://awipev-co2.obs-vlfr.fr -->
<!-- ![ ](images/web_page.png) -->

@@

# **Availability of data**
:::: {style="display: flex;"}
::: {class='col-md-4'}
## Many challenges:

@@

- data usable 50 to 76% of the time during the period of measurement
- pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months
:::
::: {class='col-md-8'}

![ ](figures/availability.png){ width=70% }
:::
::::

***

# **Nutrients**
:::: {style="display: flex;"}
::: {class='col-md-4'}

- 90 phosphate and 133 silicate data kindly provided by van de Poll (unpubl.)
- PO4 and Si vary by a factor 10 along a composite year
- disregarding nutrients does not generate large differences:
  - pCO2-AT pair, differences in pH, CT and OmegaA: < 0.001 unit, 0.7 umol/kg and <0.01
  - CT-AT pair: differences in pH, pCO2 and OmegaA: 0.002 units, 1.5 uatm and <0.01
:::
::: {class='col-md-8'}
![ ](figures/nutrients.png)
:::
::::

***

:::: {.blackbox data-latex=""}
# **K1 and K2**

- Big issue in the Arctic due to low temperature and salinity (Sulpis et al., 2020) 
- Lueker et al. (2000), which are recommended by the community (Jiang et al., 2022) derived in lab conditions with no temperature value < 2 °C. Overestimates K1 and K2 at temperatures below about 8 °C
- Millero et al. (2002) and Sulpis et al. (2020) based on large (> 900) field data sets that include cold temperature values
- Papadimitriou et al. (2018), obtained in the laboratory, also cover cold temperatures
- Formulations of Papadimitriou et al. (2018) perform better here but seldom used
- Hence, we used the facto standard of Lueker et al. (2000)
:::

***

# **Total alkalinity vs salinity relationship**
r2 = 0.81

![ ](figures/p_at_s.png){ width=50% height=50% }

***

# **Time series of key variables**
![ ](figures/time_series.png)

***

# **Monthly means**
![ ](figures/ts_boxplots.png)

***

@@

<!-- ::: {style="text-align:center" markdown="1"} -->
![ ](figures/pco2_calc_meas.png){ width=70% height=70% }
<!-- ::: -->

***

@@

:::: {style="display: flex;"}
::: {class='col-md-5'}

- Weird profiling approach
- Salinity in the bottom layer (8 to 12 m) is up to 1 unit higher than in the surface layer (0 to 4 m) in summer, 0.7 unit lower in Dec and similar in both layers at other times
- Temperature is lower by up to 2.7°C in the deep layer from Mar to Sep and higher by up to 2.4 °C in Nov-Jan
- Density is almost always higher in the bottom than in the surface layer.

:::
::: {class='col-md-5'}

  ![ ](figures/deltas.png)
:::
::::

***

# **Air-sea CO<sub>2</sub> flux**

  ![ ](figures/air-sea_CO2_flux.png)

***

:::: {.blackbox data-latex=""}
# **Conclusion**

- **Positive aspects**: 
  - First multi-year, high-frequency time series of the carbonate system in the Arctic 
  - Excellent support from AWIPEV staff until 2020
- **Logistical difficulties**:
  - Winter sampling essential
  - Challenging environment; divers needed to sort out issues
  - Difficult and costly to gather a team and organize field trip on short notice
  - New regulation for the use HgCl<sub>2</sub> and transportation of poisoned samples

:::

  ***

:::: {.blackbox data-latex=""}
# **Acknowledgements**

>>>>

------------------------------------------------------------------------

@@

![](images/map_fransner.png){width="50%"} ![](images/pH_fransner.png){width="50%"}

------------------------------------------------------------------------

# **Study location**

![](images/map_platt.png)

@@

------------------------------------------------------------------------

::: {.blackbox data-latex=""}
## **Instrumental set-up**

@@

::: {style="display: flex;"}
::: col-md-4
![](images/container.png)
:::

::: col-md-4
![](images/intake.png)
:::

::: col-md-4
![](images/ferrybox.jpg)
:::
:::

## **Instruments on the REMOS**

![](images/seafet.png)

------------------------------------------------------------------------

<!-- # No longer in real-time: https://awipev-co2.obs-vlfr.fr -->

<!-- ![ ](images/web_page.png) -->

@@

# **Availability of data**

::: {style="display: flex;"}
::: col-md-4
## Many challenges:

@@

-   data usable 50 to 76% of the time during the period of measurement
-   pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months
:::

::: col-md-8
![](figures/availability.png){width="70%"}
:::
:::

------------------------------------------------------------------------

# **Nutrients**

::: {style="display: flex;"}
::: col-md-4
-   90 phosphate and 133 silicate data kindly provided by van de Poll (unpubl.)
-   PO4 and Si vary by a factor 10 along a composite year
-   disregarding nutrients does not generate large differences:
    -   pCO2-AT pair, differences in pH, CT and OmegaA: \< 0.001 unit, 0.7 umol/kg and \<0.01
    -   CT-AT pair: differences in pH, pCO2 and OmegaA: 0.002 units, 1.5 uatm and \<0.01
:::

::: col-md-8
![](figures/nutrients.png)
:::
:::

------------------------------------------------------------------------

::: {.blackbox data-latex=""}
# **K1 and K2**

-   Big issue in the Arctic due to low temperature and salinity (Sulpis et al., 2020)
-   Lueker et al. (2000), which are recommended by the community (Jiang et al., 2022) derived in lab conditions with no temperature value \< 2 °C. Overestimates K1 and K2 at temperatures below about 8 °C
-   Millero et al. (2002) and Sulpis et al. (2020) based on large (\> 900) field data sets that include cold temperature values
-   Papadimitriou et al. (2018), obtained in the laboratory, also cover cold temperatures
-   Formulations of Papadimitriou et al. (2018) perform better here but seldom used
-   Hence, we used the facto standard of Lueker et al. (2000)
:::

------------------------------------------------------------------------

# **Total alkalinity vs salinity relationship**

r2 = 0.81

![](figures/p_at_s.png){width="50%" height="50%"}

------------------------------------------------------------------------

# **Time series of key variables**

![](figures/time_series.png)

------------------------------------------------------------------------

# **Monthly means**

![](figures/ts_boxplots.png)

------------------------------------------------------------------------

@@

<!-- ::: {style="text-align:center" markdown="1"} -->

![](figures/pco2_calc_meas.png){width="70%" height="70%"} <!-- ::: -->

------------------------------------------------------------------------

@@

::: {style="display: flex;"}
::: col-md-5
-   Weird profiling approach
-   Salinity in the bottom layer (8 to 12 m) is up to 1 unit higher than in the surface layer (0 to 4 m) in summer, 0.7 unit lower in Dec and similar in both layers at other times
-   Temperature is lower by up to 2.7°C in the deep layer from Mar to Sep and higher by up to 2.4 °C in Nov-Jan
-   Density is almost always higher in the bottom than in the surface layer.
:::

::: col-md-5
![](figures/deltas.png)
:::
:::

------------------------------------------------------------------------

# **Air-sea CO**<sub>2</sub> flux

![](figures/air-sea_CO2_flux.png)

------------------------------------------------------------------------

::: {.blackbox data-latex=""}
# **Conclusion**

-   **Positive aspects**:
    -   First multi-year, high-frequency time series of the carbonate system in the Arctic
    -   Excellent support from AWIPEV staff until 2020
-   **Logistical difficulties**:
    -   Winter sampling essential
    -   Challenging environment; divers needed to sort out issues
    -   Difficult and costly to gather a team and organize field trip on short notice
    -   New regulation for the use HgCl<sub>2</sub> and transportation of poisoned samples
:::

------------------------------------------------------------------------

::: {.blackbox data-latex=""}
# **Acknowledgements**
